\bf Comparing the Power of Plot Designs to Reveal Correlation

### 2015-12-18 paper/paper.Rnw
Fixed

\begin{table}[htp]
\caption{Weighted Mixed Effects Logit Model for the predicted power of plot design. Sample size for scatter plot evaluations: 900, overlaid lines: 949, total: 1849. Default plot design is an overlaid lines type. The model is fitted using the glimmix procedure in SAS. Subjects with less than ten lineup evaluations were removed from the sample.} %Sign = 1 if correlation > 0, 0 otherwise. Each plot design is estimated separately. Results must be transformed via the logit link function to generate a power prediction. Subjects with less than ten lineup evaluations were removed from the sample.
\label{tab1}
\centering
<<powerfit, dependson='setup', results='asis', echo=FALSE, message=FALSE, error=FALSE, warning=FALSE>>=
full$subj_id <- factor(full$ip_address, labels=1:207)

@@

\begin{figure}[htbp]
 \centering
<<powermodel, dependson='powerfit', fig.height=6, fig.width=6, out.width='0.7\\textwidth', echo=FALSE>>=
rabs <- seq(0,0.9,0.02)
t <- c(12, 24, 48, 96)
#pred <- data.frame(expand.grid(rabs=rabs, t=t, alpha=log(.05/0.95), rsgn=c(0,1),
#                                      smoothed=c(0,1), plot=c(0,1),
#                                      subj_id=full.sub$subj_id))
#write.csv(pred, "sas/predgrid.csv") # these lines are done, but its a large file so commented out for knitr
#Code exported to sas, see sas/model\ fit.sas
prediction <- read.csv("sas/predfit.csv") #Large file, very slow
rownames(prediction) <- c("rabs", "t", "alpha", "rsgn", "smoothed", "plot", "subj_id", "weights", "detected", "RandomEf", "FixedEf", "resid")
resid <- subset(prediction, detected==0 | detected==1)
prediction <- mutate(prediction, r = ifelse(rsgn==1, rabs, -rabs), plot = ifelse(plot==1, "Overlaid Lines", "Scatterplot"), plot = ifelse(smoothed==1, paste(plot, "(Smoothed)", sep=" "), plot))
prediction <- select(prediction, rabs, t, rsgn, smoothed, plot, subj_id, RandomEf, FixedEf)
prediction <- mutate(prediction, RandomEf = exp(RandomEf)/(1+exp(RandomEf)), FixedEf = exp(FixedEf)/(1+exp(FixedEf)))

@@

\begin{figure}
  \centering
<<residuals, dependson='powerfit', fig.height=4, fig.width=6, out.width='0.7\\textwidth', echo=FALSE, warning=FALSE>>=
resids <- subset(resid, plot==1)
residl <- subset(resid, plot==0)
#resids[842:843] <- NA  #fix residual stuff later
#resid <- data.frame(line = residl, scatter = resids)
#p1b <- ggplot(data=resid[1:841,]) + geom_histogram(aes(y=..density.., x=scatter)) + labs(title="Scatter plot", x="residual", y=element_blank())
#p2b <- ggplot(data=resid) + geom_histogram(aes(y=..density.., x=line))+ labs(title="Overlaid Lines", x="residual", y=element_blank())
#grid.arrange(p1b, p2b, ncol=2, top = "Residual density plots")
@
  \label{residuals}
  \caption{Histograms of residuals for both the scatter plot (left) and the overlaid lines (right).}
\end{figure}

@@

\begin{table}
\label{tab2}
\centering
\caption{Linear mixed model fit for time taken to make a selection, default plot style is overlaid lines.}
<<timefit, dependson='powerfit', echo=FALSE, results='hide', message=FALSE, error=FALSE, warning=FALSE>>=
timelmer <-  lmer(log_time ~ smoothed + r + n + rsgn*r + plot + plot*smoothed 
                  + plot*r + plot*n + plot*rsgn*r + plot*correct + (1|subj_id), data=full.sub)
time.fit <- summary(timelmer)$coefficients
pv <- function(x){
  p <- 2*(1-pt(x, 1835))
}
p.value <- sapply(time.fit[,3], pv)
time.fit <- cbind(time.fit, p.value)
time.fit <- time.fit[c(1, 2, 4, 3, 5, 8, 7, 6, 9, 11, 10, 12, 14, 13),] #separate into main effects then interaction effects in same order
rownames(time.fit) <- c("Intercept", "Smoothed", "t", "r", "sign(r)", "r*sign(r)", "correct", "Plot", "Plot*Smoothed", "Plot*t", "Plot*r", "Plot*sign(r)", "Plot*r*sign(r)", "Plot*correct")
kable(time.fit[1:7,], format="latex", caption="Main Effects", digits=2)
kable(time.fit[8:14,], format="latex", caption="Interaction Effects", digits=2)
@
\end{table}

>>>>

\begin{table}[htp]
\caption{Weighted Mixed Effects Logit Model for the predicted power of plot design. Sample size for scatter plot evaluations: 900, overlaid lines: 949, total: 1849. Default plot design is an overlaid lines type. The model is fitted using the glimmix procedure in SAS. Subjects with less than ten lineup evaluations were removed from the sample.} %Sign = 1 if correlation > 0, 0 otherwise. Each plot design is estimated separately. Results must be transformed via the logit link function to generate a power prediction. Subjects with less than ten lineup evaluations were removed from the sample.

\label{tab1}
\centering
<<powerfit, dependson='setup', results='asis', echo=FALSE, message=FALSE, error=FALSE, warning=FALSE>>=
full$subj_id <- factor(full$ip_address, labels=1:207)

@@

\begin{figure}[htbp]
 \centering
<<powermodel, dependson='powerfit', fig.height=6, fig.width=6, out.width='0.7\\textwidth', echo=FALSE>>=
rabs <- seq(0,0.9,0.02)
t <- c(12, 24, 48, 96)
#pred <- data.frame(expand.grid(rabs=rabs, t=t, alpha=log(.05/0.95), rsgn=c(0,1),
#                                      smoothed=c(0,1), plot=c(0,1),
#                                      subj_id=full.sub$subj_id))
#write.csv(pred, "sas/predgrid.csv") # these lines are done, but its a large file so commented out for knitr
#Code exported to sas, see sas/model\ fit.sas
prediction <- read.csv("sas/predfit.csv") #Large file, very slow
colnames(prediction) <- c("rabs", "t", "alpha", "rsgn", "smoothed", "plot", "subj_id", "weights", "detected", "RandomEf", "FixedEf", "residual")
glmm.resid <- subset(prediction, detected==0 | detected==1)
prediction <- mutate(prediction, r = ifelse(rsgn==1, rabs, -rabs), plot = ifelse(plot==1, "Overlaid Lines", "Scatterplot"), plot = ifelse(smoothed==1, paste(plot, "(Smoothed)", sep=" "), plot))
prediction <- select(prediction, rabs, t, rsgn, smoothed, plot, subj_id, RandomEf, FixedEf)
prediction <- mutate(prediction, RandomEf = exp(RandomEf)/(1+exp(RandomEf)), FixedEf = exp(FixedEf)/(1+exp(FixedEf)))

@@

\begin{figure}
  \centering
<<residuals, dependson='powerfit', fig.height=4, fig.width=6, out.width='0.7\\textwidth', echo=FALSE, warning=FALSE>>=
p1b <- ggplot(data=subset(glmm.resid, plot==1)) + geom_histogram(aes(y=..density.., x=residual)) + labs(title="Scatter plot", x="residual", y=element_blank())
p2b <- ggplot(data=subset(glmm.resid, plot==0)) + geom_histogram(aes(y=..density.., x=residual))+ labs(title="Overlaid Lines", x="residual", y=element_blank())
grid.arrange(p1b, p2b, ncol=2, top = "Residual density plots")
@
  \label{residuals}
  \caption{Histograms of residuals for both the scatter plot (left) and the overlaid lines (right).}
\end{figure}

@@

\begin{table}
\label{tab2}
\centering
\caption{Linear mixed model fit for time taken to make a selection, default plot style is overlaid lines.}

<<timefit, dependson='powerfit', echo=FALSE, results='hide', message=FALSE, error=FALSE, warning=FALSE>>=
timelmer <-  lmer(log_time ~ smoothed + r + n + rsgn*r + plot + plot*smoothed 
                  + plot*r + plot*n + plot*rsgn*r + plot*correct + (1|subj_id), data=full.sub)
time.fit <- summary(timelmer)$coefficients
pv <- function(x){
  p <- 2*(1-pt(x, 1835))
}
p.value <- sapply(time.fit[,3], pv)
time.fit <- cbind(time.fit, p.value)
time.fit <- time.fit[c(1, 2, 4, 3, 5, 8, 7, 6, 9, 11, 10, 12, 14, 13),] #separate into main effects then interaction effects in same order
rownames(time.fit) <- c("Intercept", "Smoothed", "t", "r", "sign(r)", "r*sign(r)", "correct", "Plot", "Plot*Smoothed", "Plot*t", "Plot*r", "Plot*sign(r)", "Plot*r*sign(r)", "Plot*correct")
kable(time.fit[1:7,], format="latex", caption="Main Effects", digits=2)
kable(time.fit[8:14,], format="latex", caption="Interaction Effects", digits=2)
@
\end{table}
